---
title: "hw03"
author: "Naidan Tu"
date: "2/22/2021"
output: 
  github_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tibble)
library(dplyr)
library(tidyr)
library(ggplot2)
```

# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.

```{r}
dictionary <- readr::read_csv("green_dictionary.csv")
green_data <- readr::read_csv("green_data.csv")
```

For your assignment, do the following.

  1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). 
     Is anything unusual?
     
```{r}
as_tibble(green_data) # BMW: You didn't assign this result?
green_data %>% 
  summary()
```

  There are some -99 values that need to be recoded into NA.

```{r}
green_data[green_data == -99] <- NA
# or
# green_data <- 
#   mutate(across(everything(),
#                 ~ na_if(.x, -99)))

green_data %>% 
  summary()
```
 
 
  2. Compute total scores for the four scales. 
     Recode variables as needed.
     
```{r}
reverse <- dictionary %>%
  filter(Keying == -1 | Keying == -2) %>%
  pull(Item)
reverse

green_data %>%
  mutate(
    across(all_of(reverse),
           ~ recode(.x, "5" = 1, "4" = 2, "3" = 3, "2" = 4, "1" = 5))
  )

green_data <- green_data %>% 
  rowwise() %>% 
  mutate(green=sum(c_across(green1:green5), na.rm = T), # BMW: Use mean() instead of sum() when computing total scores--it's more robust to missing data.
         comp=sum(c_across(comp1:comp10), na.rm = T),
         intel=sum(c_across(intel1:intel10), na.rm = T),
         open=sum(c_across(open1:open10), na.rm = T)) 

green_data[green_data == 0] <- NA
```

  3. Rescale the variables so that they go from 0-100 instead of the original range.
     Name the recaled variables `*_pomp`.

```{r}
green_pomp=((green_data$green-5)/(25-5))*100
comp_pomp=((green_data$comp-10)/(50-10))*100
intel_pomp=((green_data$intel-10)/(50-10))*100
open_pomp=((green_data$open-10)/(50-10))*100
green_data1 <- cbind(green_data, green_pomp, comp_pomp, intel_pomp, open_pomp)
```     

  4. Make plots that illustrate the distributions of the 4 POMP-scored variables.
  
     The plots show that the four variables are normally distributed.
  
```{r}
ggplot(green_data1) +
  aes(x = green_pomp) +
  geom_histogram(binwidth = 1)

ggplot(green_data1) +
  aes(x = comp_pomp) +
  geom_histogram(binwidth = 1)

ggplot(green_data1) +
  aes(x = intel_pomp) +
  geom_histogram(binwidth = 1)

ggplot(green_data1) +
  aes(x = open_pomp) +
  geom_histogram(binwidth = 1)
```

  5. Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
     
     The plots show that the linear relationships between green reputation and each personality trait are            different between students group and non-students group.
     
```{r}
green_data1$student <- as.factor(green_data1$student)

ggplot(na.omit(green_data1)) +
  aes(x = comp_pomp,
      y = green_pomp,
      fill = student,
      color = student) +
  geom_point() +
  geom_smooth(method = "lm", aes(group=student)) 

ggplot(na.omit(green_data1)) +
  aes(x = intel_pomp,
      y = green_pomp,
      fill = student,
      color = student) +
  geom_point() +
  geom_smooth(method = "lm", aes(group=student)) 

ggplot(na.omit(green_data1)) +
  aes(x = open_pomp,
      y = green_pomp,
      fill = student,
      color = student) +
  geom_point() +
  geom_smooth(method = "lm", aes(group=student)) 
```

  6. Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).
  
  The green reputation score distributions are similar between the two groups. The range and the median of the green reputation score are also similar. Student group probably has more people than student group.
  
```{r}
ggplot(na.omit(green_data1)) +
  aes(y = student,
      x = green_pomp,
      fill = student,
      color = student) +
  geom_jitter(height = .15) + # BMW: Be sure to include width = 0 to not add any noise on the x axis
  geom_boxplot(color = "black",
               alpha = .5,
               width = .1,
               size = .5) +
  ggdist::stat_slab(height = .3,
                    color = "black",
                    size = .2,
                    alpha = .5,
                    position = position_nudge(y = .2))
```

  7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
  
  For green reputation scores, student group has slightly lower mean scores and more variations within group.
  For compassion scores, student group has slightly lower mean scores and less variations within group.
  For intellectual curiosity scores, student group has higher mean scores and less variations within group.
  For openness to experiences scores, student group has higher mean scores and more variations within group.

```{r}
green_data1 %>%
  filter(!is.na(student)) %>%
  group_by(student) %>%
  summarize(across(
    c(green_pomp:open_pomp),
    list(
      mean = ~ mean(.x, na.rm = T),
      sd = ~ sd(.x, na.rm = T),
      median = ~ median(.x, na.rm = T),
      min = ~ min(.x, na.rm = T),
      max = ~ max(.x, na.rm = T)
    )
  ))
```  
  
In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.
