---
title: "Beautifying RMarkdown"
author: "Naidan Tu"
date: "`r format(Sys.Date(), '%b %d %Y')`"
output: 
  html_document:
    theme: lumen
    highlight: haddock
    code_folding: hide
    toc: true
    toc_float: true
    toc_dept: 3
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
library(ggplot2)
library(dplyr)
```

## The Surprising Truth about `mpg`

### `mpg`: The Figure
Add a code chunk that uses the `ggplot2::mpg` dataset to plot `displ` against `hwy` (highway mpg), with points colored by `manufacturer` and shaped by `year`.
```{r}
mpg$year <- as.factor(mpg$year)
ggplot(mpg) +
  aes(x = displ,
      y = hwy,
      fill = manufacturer,
      color = manufacturer,
      shape = year) +
  geom_point()
```

### `mpg`: The Table

Add a second code chunk that gives a summary table with the **mean** and **sd** for `displ` and `hwy` for each year.

Around each piece of output, add a brief description.

We will examine how various options change the rendered HTML output.
```{r}
mpg %>% 
  group_by(year) %>%
  summarize(mu_displ=mean(displ, na.rm = T), sd_displ=sd(displ, na.rm = T), 
            mu_hwy=mean(hwy, na.rm = T), sd_hwy=sd(hwy, na.rm = T))
```

There is slightly increase in average displ in 2008 comparing to 1999, and there is no huge difference in hwy between 1999 and 2008.

## Resources

Here are two general RMarkdown how-to books that are chock-full of great info:

  - https://bookdown.org/yihui/rmarkdown/
  - https://bookdown.org/yihui/rmarkdown-cookbook/
  
## Code Highlighting

