---
title: "Beer Advocate: ABV and quality ratings"
author: "Naidan Tu"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
```

For this activity, download the data file at this location to the `data` subfolder in your `participation` folder. 
This dataset contains information about different catagories of beer as rated on <beeradvocate.com>.
The data are originally from [here](http://scottjanish.com/relationship-of-abv-to-beer-scores/).

```{r}
if (!dir.exists( here::here("participation", "data") ) ) {
  dir.create( here::here("participation", "data"), recursive = T)
}
csv_url <- "https://raw.githubusercontent.com/USF-Psych-DataSci/Classroom/master/data/beer-advocate.csv"
download.file(
  csv_url, 
  here::here("participation", "data", "datafile.csv"), 
  mode = "wb"
)

url <- "https://raw.githubusercontent.com/USF-Psych-DataSci/Classroom/master/data/beer-advocate.csv"
dat <- read_csv(url)
dat <- dat[-(101:102),]
dat$`Average ABV` <- as.double(dat$`Average ABV`)
dat
ggplot(dat) +
  aes(x = 'Average ABV',
      y = rAVG) +
  geom_point() +
  geom_jitter()
dat %>% 
  summarize(muABV=mean(`Average ABV`), sigmaABV=sd(`Average ABV`), 
            murAVG=mean(rAVG), sigmarAVG=sd(rAVG),
            cor(`Average ABV`, rAVG))
na=c("", "NA", "Non-alcoholic")
```

The dataset contains 3 variables:

  1. Beer category
  2. Average alcohol by volume (ABV) in percentage (%)
  3. Average quality rating (rAVG) on a 1–5 scale
  
You should write a script to do the following:

  1. Download the dataset with an appropriate filename.
  2. Import the dataset into R.
     Be sure to check for any importing problems and correct as needed.
  3. Make a figure illustrating the relationship between ABV and beer quality.
  4. Compute a summary table with the mean and SD of each variable, along with their correlation.
  5. Describe the results.
  
ABV and beer quality are positively correlated with a correlation equals to 0.48. The variance of beer quality is relatively small comparing to ABV.
